Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-21 chapters/introduction/introduction.tex
minor change

\subsection{General Probabilistic Model for Geo-Calibration}
The complete camera geo-calibration detects the camera
geographic location, pose, and focal length of the camera.  We
design a general model to estimate the probability over these
geo-calibration parameters: First, we model the relationship between the
image projection of the scene and the geo-calibration parameters. This
relationship can be described by the pin-hole model, and
the geographic location of the camera.
We then construct a scoring function to measure the ``fitness'' between the
calibration parameters and the observation of the image. 
The scoring function is proportional to the probability distribution
of the camera parameters. We propose a Markov Chain Monte
Carlo (MCMC) sampling approach to approximate the underlying
probability distribution over the full geo-calibration of the camera.
Our model is a general architecture, which can take different
constraints to form the scoring function. The details about this model
can be found in \chapref{mcmc}.

\subsection{Developing Constraint Functions}
In our general model, the scoring function is defined as a linear
combination of multiple constraint functions.
In the rest of the work, we focus on developing good constraint
functions for different set of calibration parameters.

\begin{itemize}[noitemsep]
  \item \textbf{Constraint for Horizon Line and Vanishing Points:}
  We first estimate camera roll and pitch angles. Assuming the intrinsic
  parameters are known, camera roll and pitch angles can be
  derived from the horizon line position in the image. Compared to
  directly detecting the camera pose, identifying horizon line is easier
  because it is tightly related to the appearance
  of the scene. In our work, we create a new method using CNN to
  estimate the prior distribution of the horizon line. We assign
  a probability to each horizon line by measuring their consistences
  with vanishing points detected using traditional statistic methods.
  We present the algorithm details in \chapref{fasthorizon}.
  \newline

  \item \textbf{Constraint for Time and Coarse Geographic Locations:}
  In this work, we demonstrate to estimate the capture time and the
  camera geographic location given the input image.
  Our network has two heads to predict the image
  capture time and the geographic location jointly.
  For time estimation, our network is able to predict the
  joint distribution over the month of the year and the global hour of the
  day when the input image has been captured.
  For camera geo-localization, We provide two approaches to obtain the
  probability distribution over the camera geographic location. Most
  straightforwardly, our network estimate the categorical distribution
  over location of the world, which is represented as a $N \times M$
  meshgrid. Better results can be procured with image capture time as
  auxiliary input (if it is known). 
  %Our algorithm can also compute the probability at arbitrary
  %geographic location, with lower accuracy than the straightforward
  %method.
  We will present the algorithm details in \chapref{whenwhere}.
  \newline

  \item \textbf{Constraint for Fine Geographic Locations and Orientations:}
  In our previous method, we present that our algorithm can estimate
  the camera location distribution in low-res world division. In this
  work we focus on refining the geo-localization results with the help
  of overhead imagery and on estimating geo-orientation of the camera. 
  We first learn to segment the ground scene from its paired aerial image.
  When refining the camera geographic location, we compare the
  semantic layout of the ground image with the semantic layout
  transferred from overhead images, which are sampled in different
  locations and orientation angles. The optimal prediction is found when the
  semantic layouts from these two sources match best. For probabilistic
  outputs, we assign a score to each location and orientation setting,
  based on how well the semantic layouts match to each other. We will
  present the algorithm details in \chapref{crosstransf}.
  \newline

>>>>

\subsection{General Probabilistic Model for Geo-Calibration}
We design a general model to estimate the probability over all
geo-calibration parameters. First, we model the process of projecting
from the scene at given location, time, and in given camera pose.
%This the appearance of the image frame are determined by the pin-hole
%model and the geographic location of the camera.
We use a scoring function to measure the ``fitness'' between these
geo-calibration parameters and the appearance of the image. 
The scoring function is proportional to the probability distribution
over the geo-calibration parameters, but the denominator is unknown. We
then propose a Markov Chain Monte Carlo (MCMC) sampling approach to
approximate the underlying probability distribution.
Our model is a general architecture, which can take different
constraints to form the scoring function. The details of this model
can be found in \chapref{mcmc}.

\subsection{Developing Constraint Functions}
In the general model, we define the scoring function is as a weighted
summation of a series of constraint functions.
In the rest of the work, we focus on developing good constraint
functions for different set of geo-calibration parameters. 
A constraint function outputs a score or probability for some given
geo-calibration parameters conditional on the input image.

\begin{itemize}[noitemsep]
  \item \textbf{Constraint for Camera Pose:}
  In this constraint we model the camera roll and pitch angles.
  Assuming the intrinsic parameters are known, camera roll and pitch
  angles can be derived from the horizon line position on the image.
  Compared to directly detecting the camera pose, identifying horizon
  line is easier because it is tightly related to the scene layout.
  In our work, we create a new method using CNN to estimate the
  prior distribution over the horizon line. We assign a probability to
  each horizon candidate sampled from the prior distribution by
  measuring their consistences with vanishing points detected using
  traditional statistic methods. We present the algorithm details in
  \chapref{fasthorizon}.  \newline

  \item \textbf{Constraint for Time and Coarse Location:}
  In this work, we demonstrate to estimate probability over the
  capture time and the camera geographic location given the input image.
  Our network has two branches which predict the image
  capture time and the geographic location simultaneously.
  For time estimation, our network is able to predict the
  joint distribution over the month of the year and the UTC hour of the
  day when the input image has been captured.
  For coarse camera geo-localization, We provide two approaches to
  obtain the probability distribution over the camera geographic
  location. Most straightforwardly, our network outputs the discrete
  distribution over the location in the world, which is uniformly
  divided as a 2D meshgrid. Better results can be procured with the
  image capture time as auxiliary input (if it is known). 
  We present the algorithm details in \chapref{whenwhere}.
  \newline

  \item \textbf{Constraint for Fine Location and Orientation:}
  In our previous method, we present that our algorithm can estimate
  the camera location distribution in low-res world division. In this
  work we focus on refining the geo-localization results with the help
  of overhead imagery and on estimating the geo-orientation of the camera. 
  We trained our network with cross-view pairs.
  We first learn to deduce the semantic layout of the ground
  scene from the associated aerial image.
  Given a geographic location and orientation, we sample the aerial
  image, then compare its semantic layout of the ground scene
  with the semantic layout of the query image (ground image).
  We assign a score to that location and orientation by matching these
  two semantic layouts.
  We present the algorithm details in \chapref{crosstransf}.
  \newline
